---
title: "Hard-to-reach analysis and results"
author: "Juho Luoma"
date: "`r Sys.Date()`"
output: 
  html_document:
    fig_crop: false
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(crop = TRUE)
```

```{r, echo=FALSE,include=FALSE}


## Functions

source(
  paste0(here::here(),"/Public Code/htr_functions.R")
)



```

```{r, echo=F,include=F}

# Needed libraries
library(tidyverse)
library(psych)
library(lme4)

library(irrCAC)
library(irr)
library(RStata)


## Get the data
path = here::here("Public data")

data = read.csv(paste0(path,"/LAKANA Hard-to-reach dataset.csv"))



## Making data dictionary
# data_dict = cbind.data.frame( names(data),
#                   c("---",
#                     "Unique Village Identifier",
#                     "Numerical pseudonym for the District",
#                     "Numerical pseudonym for the cscom",
#                     "Numerical pseudonym for the Village name",
#                     "Overall estimate of hardness to reach",
#                     "Estimate of village residents’ access to health care",
#                     "How difficult is it to transport equipment to the village in the rainy season?",
#                     "How difficult is it to transport equipment to the village in the non-rainy season?",
#                     "Estimate of travel time to the village on rainy season",
#                     "Estimate of travel time to the village on non-rainy season",
#                     "Difficulty of the terrain or road on rainy season",
#                     "Difficulty of the terrain or road on non-rainy season",
#                     "Can the village be rached by large, motorized vehicle",
#                     "Are there any public transportation possibilities for the residents?",
#                     "Numerical pseudonym for the username",
#                     "App start time from app metadata",
#                     "Numerical pseudonym for the rater",
#                     "Number of villages evaluated in a survey round",
#                     "Time taken to fill the survey round",
#                     "Workload estimate",
#                     "Distance from the nearest health facility",
#                     "Outreach program status",
#                     "Travel time by car (minutes) from OpenStreetMap API",
#                     "Mean monthly rainfall (mean mm/month) from Open-Meteo API",
#                     "Sum of Person-time in a village",
#                     "Number of deaths in a village",
#                     "All-item composite score",
#                     "Two-item composite score",
#                     "Condition of the roads on rainy season",
#                     "Condition of the roads in the non-rainy season",
#                     "Difficulty of the terrain on rainy season",
#                     "Difficulty of the terrain on non-rainy season",
#                     "Numerical pseudonym for the electronic form"),
#                   c("---",
#                     "Alphanumeric string",
#                     "Integer",
#                     "Integer",
#                     "Integer",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer; [1=under one hour, 2=1-2 hours, 3=3-4 hours, 4=4-5 hours, 5=over 5 hours]",
#                     "Integer; [1=under one hour, 2=1-2 hours, 3=3-4 hours, 4=4-5 hours, 5=over 5 hours]",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer; [0=No, 1=Yes, Unknown=99]",
#                     "Integer; [0=No, 1=Yes, Unknown=99]",
#                     "Integer",
#                     "Datetime",
#                     "Integer",
#                     "Integer",
#                     "Minutes",
#                     "Integer; [1-3]",
#                     "Double",
#                     "Integer; [0=Standard,1=Advanced]",
#                     "Double",
#                     "Double",
#                     "Float",
#                     "Integer",
#                     "Integer; Sum of survey itmes",
#                     "Integer; Sum of two items",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer; [1-5]",
#                     "Integer"))
# names(data_dict) = c("Variable names","Description","Format")
# 
# openxlsx::write.xlsx(data_dict,"LAKANA Hard-to-reach data dictionary.xlsx")


## Mortality result
composite_mort_mod = glmer(eligibleDeath~ scale(composite_full)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_composite_mort_mod = glmer(eligibleDeath~ scale(composite_full) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

estimate_comp = summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_comp_low = as.numeric(estimate_comp) + 
  c(
    as.numeric(-1.96*summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_comp_high = as.numeric(estimate_comp) + as.numeric(1.96*summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())

p = summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_comp = summary(unadj_composite_mort_mod)$coef[-1,1] %>% 
   as.numeric()   ## to output

unadj_CI_comp_low = as.numeric(unadj_estimate_comp) + 
  c(
    as.numeric(-1.96*summary(unadj_composite_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_comp_high = as.numeric(unadj_estimate_comp) + as.numeric(1.96*summary(unadj_composite_mort_mod)$coef[-1,2] )



mortality_res_df = data.frame(
  "Model" = c(" ", "Model 1"),
  "Model.Covariates" = c("Composite variable (full)",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_comp %>% exp() %>% round(2)," (",
    unadj_CI_comp_low %>% exp() %>% round(3),"-",
    unadj_CI_comp_high %>% exp() %>% round(3),")"
  )," " ),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_comp %>% exp() %>% round(2)," (",
    CI_comp_low %>% exp() %>% round(3),"-",
    CI_comp_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))




### Trimmed composite score
## Mortality result
composite_mort_mod = glmer(eligibleDeath~ scale(composite_trim)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_composite_mort_mod = glmer(eligibleDeath~ scale(composite_trim) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

estimate_comp = summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_comp_low = as.numeric(estimate_comp) + 
  c(
    as.numeric(-1.96*summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_comp_high = as.numeric(estimate_comp) + as.numeric(1.96*summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())

p = summary(composite_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_comp = summary(unadj_composite_mort_mod)$coef[-1,1] %>% 
   as.numeric()   ## to output

unadj_CI_comp_low = as.numeric(unadj_estimate_comp) + 
  c(
    as.numeric(-1.96*summary(unadj_composite_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_comp_high = as.numeric(unadj_estimate_comp) + as.numeric(1.96*summary(unadj_composite_mort_mod)$coef[-1,2] )



mortality_res_df2 = data.frame(
  "Model" = c(" ", "Model 2"),
  "Model.Covariates" = c("Composite variable (trimmed)",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_comp %>% exp() %>% round(2)," (",
    unadj_CI_comp_low %>% exp() %>% round(3),"-",
    unadj_CI_comp_high %>% exp() %>% round(3),")"
  )," " ),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_comp %>% exp() %>% round(2)," (",
    CI_comp_low %>% exp() %>% round(3),"-",
    CI_comp_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df2,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))



### Overall estimate
overall_mort_mod = glmer(eligibleDeath~ scale(hard_overall)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")
unadj_overall_mort_mod = glmer(eligibleDeath~ scale(hard_overall) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_overall = summary(overall_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_overall_low = as.numeric(estimate_overall) + 
  c(
    as.numeric(-1.96*summary(overall_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_overall_high = as.numeric(estimate_overall) + as.numeric(1.96*summary(overall_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())

p = summary(overall_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()



unadj_estimate_overall = summary(unadj_overall_mort_mod)$coef[-1,1] %>% 
   as.numeric()   ## to output

unadj_CI_overall_low = as.numeric(unadj_estimate_comp) + 
  c(
    as.numeric(-1.96*summary(unadj_overall_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_overall_high = as.numeric(unadj_estimate_comp) + as.numeric(1.96*summary(unadj_overall_mort_mod)$coef[-1,2] )



mortality_res_df3 = data.frame(
  "Model" = c(" ", "Model 3"),
  "Model.Covariates" = c("Overall assessment",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_overall %>% exp() %>% round(2)," (",
    unadj_CI_overall_low %>% exp() %>% round(3),"-",
    unadj_CI_overall_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_overall %>% exp() %>% round(2)," (",
    CI_overall_low %>% exp() %>% round(3),"-",
    CI_overall_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df3,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))


##############################
##############################
##############################


resMed_mort_mod = glmer(eligibleDeath~ scale(hard_residentsMedical)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_resMed_mort_mod = glmer(eligibleDeath~ scale(hard_residentsMedical) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

estimate_resMed = summary(resMed_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_resMed_low = as.numeric(estimate_resMed) + 
  c(
    as.numeric(-1.96*summary(resMed_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_resMed_high = as.numeric(estimate_resMed) + as.numeric(1.96*summary(resMed_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())

p = summary(resMed_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()



unadj_estimate_resMed = summary(unadj_resMed_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_resMed_low = as.numeric(unadj_estimate_resMed) + 
  c(
    as.numeric(-1.96*summary(unadj_resMed_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_resMed_high = as.numeric(unadj_estimate_resMed) + as.numeric(1.96*summary(unadj_resMed_mort_mod)$coef[-1,2] )




mortality_res_df4 = data.frame(
  "Model" = c(" ", "Model 4"),
  "Model.Covariates" = c("Residents' access to health care",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_resMed %>% exp() %>% round(2)," (",
    unadj_CI_resMed_low %>% exp() %>% round(3),"-",
    unadj_CI_resMed_high %>% exp() %>% round(3),")"
  ), " "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_resMed %>% exp() %>% round(2)," (",
    CI_resMed_low %>% exp() %>% round(3),"-",
    CI_resMed_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df4,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))



rainyTransp_mort_mod = glmer(eligibleDeath~ scale(hard_transportationEquipmentRainy)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_rainyTransp_mort_mod = glmer(eligibleDeath~ scale(hard_transportationEquipmentRainy) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

estimate_rainyTransp = summary(rainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_rainyTransp_low = as.numeric(estimate_rainyTransp) + 
  c(
    as.numeric(-1.96*summary(rainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_rainyTransp_high = as.numeric(estimate_rainyTransp) + as.numeric(1.96*summary(rainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())

p = summary(rainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()


unadj_estimate_rainyTransp = summary(unadj_rainyTransp_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_rainyTransp_low = as.numeric(unadj_estimate_rainyTransp) + 
  c(
    as.numeric(-1.96*summary(unadj_rainyTransp_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_rainyTransp_high = as.numeric(unadj_estimate_rainyTransp) + as.numeric(1.96*summary(unadj_rainyTransp_mort_mod)$coef[-1,2] )



mortality_res_df5 = data.frame(
  "Model" = c(" ", "Model 5"),
  "Model.Covariates" = c("Difficulty of equipment transportation on rainy season",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_rainyTransp %>% exp() %>% round(2)," (",
    unadj_CI_rainyTransp_low %>% exp() %>% round(3),"-",
    unadj_CI_rainyTransp_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_rainyTransp %>% exp() %>% round(2)," (",
    CI_rainyTransp_low %>% exp() %>% round(3),"-",
    CI_rainyTransp_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df5,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))



######################
######################
######################
######################




nonrainyTransp_mort_mod = glmer(eligibleDeath~ scale(hard_transportationEquipmentNonRainy)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_nonrainyTransp_mort_mod = glmer(eligibleDeath~ scale(hard_transportationEquipmentNonRainy) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_nonrainyTransp = summary(nonrainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_nonrainyTransp_low = as.numeric(estimate_nonrainyTransp) + 
  c(
    as.numeric(-1.96*summary(nonrainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_nonrainyTransp_high = as.numeric(estimate_nonrainyTransp) + as.numeric(1.96*summary(nonrainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(nonrainyTransp_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_nonrainyTransp = summary(unadj_nonrainyTransp_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_nonrainyTransp_low = as.numeric(unadj_estimate_nonrainyTransp) + 
  c(
    as.numeric(-1.96*summary(unadj_nonrainyTransp_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_nonrainyTransp_high = as.numeric(unadj_estimate_nonrainyTransp) + as.numeric(1.96*summary(unadj_nonrainyTransp_mort_mod)$coef[-1,2] )



mortality_res_df6 = data.frame(
  "Model" = c(" ", "Model 6"),
  "Model.Covariates" = c("Difficulty of equipment transportation on non-rainy season",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_nonrainyTransp %>% exp() %>% round(2)," (",
    unadj_CI_nonrainyTransp_low %>% exp() %>% round(3),"-",
    unadj_CI_nonrainyTransp_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_nonrainyTransp %>% exp() %>% round(2)," (",
    CI_nonrainyTransp_low %>% exp() %>% round(3),"-",
    CI_nonrainyTransp_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df6,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))









##################################################################
##################################################################
###################### Travel time ###############################
##################################################################
##################################################################


rainyTime_mort_mod = glmer(eligibleDeath~ scale(hard_timeTabletPlaceRainy)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_rainyTime_mort_mod = glmer(eligibleDeath~ scale(hard_timeTabletPlaceRainy) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_rainyTime = summary(rainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_rainyTime_low = as.numeric(estimate_rainyTime) + 
  c(
    as.numeric(-1.96*summary(rainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_rainyTime_high = as.numeric(estimate_rainyTime) + as.numeric(1.96*summary(rainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(rainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_rainyTime = summary(unadj_rainyTime_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_rainyTime_low = as.numeric(unadj_estimate_rainyTime) + 
  c(
    as.numeric(-1.96*summary(unadj_rainyTime_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_rainyTime_high = as.numeric(unadj_estimate_rainyTime) + as.numeric(1.96*summary(unadj_rainyTime_mort_mod)$coef[-1,2] )



mortality_res_df7 = data.frame(
  "Model" = c(" ", "Model 7"),
  "Model.Covariates" = c("Estimate of travel time during rainy season",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_rainyTime %>% exp() %>% round(2)," (",
    unadj_CI_rainyTime_low %>% exp() %>% round(3),"-",
    unadj_CI_rainyTime_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_rainyTime %>% exp() %>% round(2)," (",
    CI_rainyTime_low %>% exp() %>% round(3),"-",
    CI_rainyTime_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df7,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))



#######################
###### Non-rainy time##
#######################


nonrainyTime_mort_mod = glmer(eligibleDeath~ scale(hard_timeTabletPlaceNonRainy)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_nonrainyTime_mort_mod = glmer(eligibleDeath~ scale(hard_timeTabletPlaceNonRainy) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_nonrainyTime = summary(nonrainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_nonrainyTime_low = as.numeric(estimate_nonrainyTime) + 
  c(
    as.numeric(-1.96*summary(nonrainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_nonrainyTime_high = as.numeric(estimate_nonrainyTime) + as.numeric(1.96*summary(nonrainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(nonrainyTime_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_nonrainyTime = summary(unadj_nonrainyTime_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_nonrainyTime_low = as.numeric(unadj_estimate_nonrainyTime) + 
  c(
    as.numeric(-1.96*summary(unadj_nonrainyTime_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_nonrainyTime_high = as.numeric(unadj_estimate_nonrainyTime) + as.numeric(1.96*summary(unadj_nonrainyTime_mort_mod)$coef[-1,2] )



mortality_res_df8 = data.frame(
  "Model" = c(" ", "Model 8"),
  "Model.Covariates" = c("Estimate of travel time during non-rainy season",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_nonrainyTime %>% exp() %>% round(2)," (",
    unadj_CI_nonrainyTime_low %>% exp() %>% round(3),"-",
    unadj_CI_nonrainyTime_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_nonrainyTime %>% exp() %>% round(2)," (",
    CI_nonrainyTime_low %>% exp() %>% round(3),"-",
    CI_nonrainyTime_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df8,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))










##################################################################
##################################################################
###################### Topographical difficulty ##################
##################################################################
##################################################################

data$hard_roadconditionRainyCar = as.numeric(data$hard_roadconditionRainyCar)
rainyRoad_mort_mod = glmer(eligibleDeath~ scale(hard_roadconditionRainyCar)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_rainyRoad_mort_mod = glmer(eligibleDeath~ scale(hard_roadconditionRainyCar) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_rainyRoad = summary(rainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_rainyRoad_low = as.numeric(estimate_rainyRoad) + 
  c(
    as.numeric(-1.96*summary(rainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_rainyRoad_high = as.numeric(estimate_rainyRoad) + as.numeric(1.96*summary(rainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(rainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_rainyRoad = summary(unadj_rainyRoad_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_rainyRoad_low = as.numeric(unadj_estimate_rainyRoad) + 
  c(
    as.numeric(-1.96*summary(unadj_rainyRoad_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_rainyRoad_high = as.numeric(unadj_estimate_rainyRoad) + as.numeric(1.96*summary(unadj_rainyRoad_mort_mod)$coef[-1,2] )



mortality_res_df9 = data.frame(
  "Model" = c(" ", "Model 9"),
  "Model.Covariates" = c("Estimate of road conditions on rainy season",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_rainyRoad %>% exp() %>% round(2)," (",
    unadj_CI_rainyRoad_low %>% exp() %>% round(3),"-",
    unadj_CI_rainyRoad_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_rainyRoad %>% exp() %>% round(2)," (",
    CI_rainyRoad_low %>% exp() %>% round(3),"-",
    CI_rainyRoad_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df9,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))









#####################
### non-rainy road ##
#####################


data$hard_roadconditionNonRainyCar = as.numeric(data$hard_roadconditionNonRainyCar)
nonrainyRoad_mort_mod = glmer(eligibleDeath~ scale(hard_roadconditionNonRainyCar)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_nonrainyRoad_mort_mod = glmer(eligibleDeath~ scale(hard_roadconditionNonRainyCar) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_nonrainyRoad = summary(nonrainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_nonrainyRoad_low = as.numeric(estimate_nonrainyRoad) + 
  c(
    as.numeric(-1.96*summary(nonrainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_nonrainyRoad_high = as.numeric(estimate_nonrainyRoad) + as.numeric(1.96*summary(nonrainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(nonrainyRoad_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_nonrainyRoad = summary(unadj_nonrainyRoad_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_nonrainyRoad_low = as.numeric(unadj_estimate_nonrainyRoad) + 
  c(
    as.numeric(-1.96*summary(unadj_nonrainyRoad_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_nonrainyRoad_high = as.numeric(unadj_estimate_nonrainyRoad) + as.numeric(1.96*summary(unadj_nonrainyRoad_mort_mod)$coef[-1,2] )



mortality_res_df10 = data.frame(
  "Model" = c(" ", "Model 10"),
  "Model.Covariates" = c("Estimate of road conditions on non-rainy season",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_nonrainyRoad %>% exp() %>% round(2)," (",
    unadj_CI_nonrainyRoad_low %>% exp() %>% round(3),"-",
    unadj_CI_nonrainyRoad_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_nonrainyRoad %>% exp() %>% round(2)," (",
    CI_nonrainyRoad_low %>% exp() %>% round(3),"-",
    CI_nonrainyRoad_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df10,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))









#######################################
########## Method of transportation ###
#######################################


reachCar_mort_mod = glmer(eligibleDeath~ as.factor(hard_ReachCar)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_reachCar_mort_mod = glmer(eligibleDeath~ as.factor(hard_ReachCar) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_reachCar = summary(reachCar_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_reachCar_low = as.numeric(estimate_reachCar) + 
  c(
    as.numeric(-1.96*summary(reachCar_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_reachCar_high = as.numeric(estimate_reachCar) + as.numeric(1.96*summary(reachCar_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(reachCar_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_reachCar = summary(unadj_reachCar_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_reachCar_low = as.numeric(unadj_estimate_reachCar) + 
  c(
    as.numeric(-1.96*summary(unadj_reachCar_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_reachCar_high = as.numeric(unadj_estimate_reachCar) + as.numeric(1.96*summary(unadj_reachCar_mort_mod)$coef[-1,2] )



mortality_res_df11 = data.frame(
  "Model" = c(" ", "Model 11"),
  "Model.Covariates" = c("Village can't be reached by car",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_reachCar %>% exp() %>% round(2)," (",
    unadj_CI_reachCar_low %>% exp() %>% round(3),"-",
    unadj_CI_reachCar_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_reachCar %>% exp() %>% round(2)," (",
    CI_reachCar_low %>% exp() %>% round(3),"-",
    CI_reachCar_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df11,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))









#####################
### public transportation ##
#####################

pubTransport_mort_mod = glmer(eligibleDeath~ as.factor(hard_publicTransportation)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_pubTransport_mort_mod = glmer(eligibleDeath~ as.factor(hard_publicTransportation) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_pubTransport = summary(pubTransport_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_pubTransport_low = as.numeric(estimate_pubTransport) + 
  c(
    as.numeric(-1.96*summary(pubTransport_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_pubTransport_high = as.numeric(estimate_pubTransport) + as.numeric(1.96*summary(pubTransport_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(pubTransport_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_pubTransport = summary(unadj_pubTransport_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_pubTransport_low = as.numeric(unadj_estimate_pubTransport) + 
  c(
    as.numeric(-1.96*summary(unadj_pubTransport_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_pubTransport_high = as.numeric(unadj_estimate_pubTransport) + as.numeric(1.96*summary(unadj_pubTransport_mort_mod)$coef[-1,2] )



mortality_res_df12 = data.frame(
  "Model" = c(" ", "Model 12"),
  "Model.Covariates" = c("Village doesn't have public transportation",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_pubTransport %>% exp() %>% round(2)," (",
    unadj_CI_pubTransport_low %>% exp() %>% round(3),"-",
    unadj_CI_pubTransport_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_pubTransport %>% exp() %>% round(2)," (",
    CI_pubTransport_low %>% exp() %>% round(3),"-",
    CI_pubTransport_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df12,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))








#########################
## Terrain difficulty,rainy ###
#########################


data$hard_terrainDifficultyRainy_num = as.numeric(data$hard_terrainDifficultyRainy)
rainyTerrain_mort_mod = glmer(eligibleDeath~ scale(hard_terrainDifficultyRainy_num)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_rainyTerrain_mort_mod = glmer(eligibleDeath~ scale(hard_terrainDifficultyRainy_num) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_rainyTerrain = summary(rainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_rainyTerrain_low = as.numeric(estimate_rainyTerrain) + 
  c(
    as.numeric(-1.96*summary(rainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_rainyTerrain_high = as.numeric(estimate_rainyTerrain) + as.numeric(1.96*summary(rainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(rainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_rainyTerrain = summary(unadj_rainyTerrain_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_rainyTerrain_low = as.numeric(unadj_estimate_rainyTerrain) + 
  c(
    as.numeric(-1.96*summary(unadj_rainyTerrain_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_rainyTerrain_high = as.numeric(unadj_estimate_rainyTerrain) + as.numeric(1.96*summary(unadj_rainyTerrain_mort_mod)$coef[-1,2] )



mortality_res_df13 = data.frame(
  "Model" = c(" ", "Model 13"),
  "Model.Covariates" = c("Not-car-suitable-terrain, rainy",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_rainyTerrain %>% exp() %>% round(2)," (",
    unadj_CI_rainyTerrain_low %>% exp() %>% round(3),"-",
    unadj_CI_rainyTerrain_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_rainyTerrain %>% exp() %>% round(2)," (",
    CI_rainyTerrain_low %>% exp() %>% round(3),"-",
    CI_rainyTerrain_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df13,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))




#########################
## Terrain difficulty, non-rainy ###
#########################


data$hard_terrainDifficultyNonRainy_num = as.numeric(data$hard_terrainDifficultyNonRainy)
nonrainyTerrain_mort_mod = glmer(eligibleDeath~ scale(hard_terrainDifficultyNonRainy_num)+scale(distanceKM) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")

unadj_nonrainyTerrain_mort_mod = glmer(eligibleDeath~ scale(hard_terrainDifficultyNonRainy_num) + offset(log(totalPYR)) + (1|rater),data = data,family="poisson")


estimate_nonrainyTerrain = summary(nonrainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Estimate") %>% unlist() %>% as.numeric()   ## to output

CI_nonrainyTerrain_low = as.numeric(estimate_nonrainyTerrain) + 
  c(
    as.numeric(-1.96*summary(nonrainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())
  ) 

CI_nonrainyTerrain_high = as.numeric(estimate_nonrainyTerrain) + as.numeric(1.96*summary(nonrainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Std. Error") %>% unlist())


p = summary(nonrainyTerrain_mort_mod)$coef[-1,] %>% 
  as.data.frame() %>% 
  select("Pr(>|z|)") %>% unlist()

unadj_estimate_nonrainyTerrain = summary(unadj_nonrainyTerrain_mort_mod)$coef[-1,1] %>% as.numeric()   ## to output

unadj_CI_nonrainyTerrain_low = as.numeric(unadj_estimate_nonrainyTerrain) + 
  c(
    as.numeric(-1.96*summary(unadj_nonrainyTerrain_mort_mod)$coef[-1,2] )
  ) 

unadj_CI_nonrainyTerrain_high = as.numeric(unadj_estimate_nonrainyTerrain) + as.numeric(1.96*summary(unadj_nonrainyTerrain_mort_mod)$coef[-1,2] )



mortality_res_df15 = data.frame(
  "Model" = c(" ", "Model 15"),
  "Model.Covariates" = c("Not-car-suitable-terrain, non-rainy",
                         "Distance to the nearest health facility"),
  "Unadjusted Risk ratio (95% CI)" = c(paste0(
    unadj_estimate_nonrainyTerrain %>% exp() %>% round(2)," (",
    unadj_CI_nonrainyTerrain_low %>% exp() %>% round(3),"-",
    unadj_CI_nonrainyTerrain_high %>% exp() %>% round(3),")"
  )," "),
  "Adjusted Risk ratio (95% CI)" = paste0(
    estimate_nonrainyTerrain %>% exp() %>% round(2)," (",
    CI_nonrainyTerrain_low %>% exp() %>% round(3),"-",
    CI_nonrainyTerrain_high %>% exp() %>% round(3),")"
  ),
  "P.value" = p %>% round(4)
)


mortality_res_df = rbind.data.frame(mortality_res_df,mortality_res_df15,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))




rownames(mortality_res_df) = NULL





mortality_res_df = rbind.data.frame(mortality_res_df,
                                    data.frame(
  "Model" = c(" "),
  "Model.Covariates" = c(" "),
  "Unadjusted Risk ratio (95% CI)" = c(" "),
  "Adjusted Risk ratio (95% CI)" = c(" "),
  "P-value" = c(" ")
))






names(mortality_res_df) = c("Model","Model Covariates","Unadjusted Risk ratio (95% CI)","Adjusted Risk ratio (95% CI)","P-value")







descrTable <-data %>% select(c(hard_ReachCar,hard_publicTransportation,
                  hard_terrainDifficultyNonRainy,hard_terrainDifficultyRainy,
                  hard_roadconditionNonRainyCar,hard_roadconditionRainyCar,
                  hard_timeTabletPlaceRainy,hard_timeTabletPlaceNonRainy,
                  hard_transportationEquipmentNonRainy,hard_transportationEquipmentRainy,
                  hard_overall,hard_residentsMedical,composite_full,composite_trim)) %>% 
  dplyr::summarise_all (list(function(x) {mean(x[which( x!=99 & x!="---")] %>% as.numeric(),na.rm=T)},
                             function(x) {sd(x[which( x!=99 & x!="---")] %>% as.numeric(),na.rm=T)},
                             function(x) {min(x[which( x!=99 & x!="---")] %>% as.numeric(),na.rm=T)},
                             function(x) {max(x[which( x!=99 & x!="---")] %>% as.numeric() ,na.rm=T)},
                             function(x) {
                               length(which(x==min(x[which(  x!=99 & x!="---")],na.rm=T)) ) / length(x[which(!is.na(x[which(x!=6 & x!=99 & x!="---")]))])
                               },
                             function(x) {
                               length(which(x==max(x[which( x!=99 & x!="---")],na.rm=T)) ) / length(x[which(!is.na(x[which(x!=6 & x!=99 & x!="---")]))])
                               }) ) %>% t() %>% as.data.frame()

descrTable = cbind.data.frame(descrTable[which( grepl("_fn1",row.names(descrTable) ) ),],
                     descrTable[which( grepl("_fn2",row.names(descrTable) ) ),],
                     descrTable[which( grepl("_fn3",row.names(descrTable) ) ),],
                     descrTable[which( grepl("_fn4",row.names(descrTable) ) ),],
                     descrTable[which( grepl("_fn5",row.names(descrTable) ) ),],
                     descrTable[which( grepl("_fn6",row.names(descrTable) ) ),])

names(descrTable) = c("Mean","SD","Min","Max","%AtMin","%AtMax")
row.names(descrTable) = c("hard_ReachCar","hard_publicTransportation",
                  "hard_terrainDifficultyNonRainy","hard_terrainDifficultyRainy",
                  "hard_roadconditionNonRainyCar","hard_roadconditionRainyCar",
                  "hard_timeTabletPlaceRainy","hard_timeTabletPlaceNonRainy",
                  "hard_transportationEquipmentNonRainy","hard_transportationEquipmentRainy",
                  "hard_overall","hard_residentsMedical","composite_full","composite_trim")

descrTable





```


```{r, echo=F,include=F}
comp_ICC = getICC("composite_full")

comp_trim_ICC = getICC("composite_trim")

overall_ICC = getICC("hard_overall")

resMed_ICC = getICC("hard_residentsMedical")

transpRainy_ICC = getICC("hard_transportationEquipmentNonRainy")

transpNonRainy_ICC = getICC("hard_transportationEquipmentRainy")

roadcondnonR_ICC = getICC("hard_roadconditionNonRainyCar")

roadcondR_ICC = getICC("hard_roadconditionRainyCar")

timeRainy_ICC = getICC("hard_timeTabletPlaceRainy")

timeNonRainy_ICC = getICC("hard_timeTabletPlaceNonRainy")

terrainDiffNonR_ICC = getICC("hard_terrainDifficultyNonRainy")

terrainDiffR_ICC = getICC("hard_terrainDifficultyRainy")


ICC_df = data.frame(
  "Item" = c("Difficulty of the terrain on non-rainy season",
             "Difficulty of the terrain on rainy season",
             "Condition of the roads on rainy season",
             "Condition of the roads in the non-rainy season",
             "Estimate of travel time to the village on rainy season",
             "Estimate of travel time to the village on non-rainy season",
             "How difficult is it to transport equipment to the village in the rainy season?",
             "How difficult is it to transport equipment to the village in the non-rainy season?",
             "Overall estimate of hardness to reach",
             "Estimate of village residents’ access to health care",
             "Composite variable, full",
             "Composite variable, trim"),
  "N" = c(terrainDiffNonR_ICC$k,
          terrainDiffR_ICC$k,
          roadcondR_ICC$k,
          roadcondnonR_ICC$k,
          timeRainy_ICC$k,
          timeNonRainy_ICC$k,
          transpRainy_ICC$k,
          transpNonRainy_ICC$k,
          overall_ICC$k,
          resMed_ICC$k,
          comp_ICC$k,
          comp_trim_ICC$k),
  "Ind.ICC" = c(paste0(round(terrainDiffNonR_ICC$ICCs[1,1],3)," (",round(terrainDiffNonR_ICC$ICCs[1,2],3),", ",round(terrainDiffNonR_ICC$ICCs[1,3],3),")"),
                paste0(round(terrainDiffR_ICC$ICCs[1,1],3)," (",round(terrainDiffR_ICC$ICCs[1,2],3),", ",round(terrainDiffR_ICC$ICCs[1,3],3),")"),
                paste0(round(roadcondR_ICC$ICCs[1,1],3)," (",round(roadcondR_ICC$ICCs[1,2],3),", ",round(roadcondR_ICC$ICCs[1,3],3),")"),
                paste0(round(roadcondnonR_ICC$ICCs[1,1],3)," (",round(roadcondnonR_ICC$ICCs[1,2],3),", ",round(roadcondnonR_ICC$ICCs[1,3],3),")"),
                paste0(round(timeRainy_ICC$ICCs[1,1],3)," (",round(timeRainy_ICC$ICCs[1,2],3),", ",round(timeRainy_ICC$ICCs[1,3],3),")"),
                paste0(round(timeNonRainy_ICC$ICCs[1,1],3)," (",round(timeNonRainy_ICC$ICCs[1,2],3),", ",round(timeNonRainy_ICC$ICCs[1,3],3),")"),
                paste0(round(transpRainy_ICC$ICCs[1,1],3)," (",round(transpRainy_ICC$ICCs[1,2],3),", ",round(transpRainy_ICC$ICCs[1,3],3),")"),
                paste0(round(transpNonRainy_ICC$ICCs[1,1],3)," (",round(transpNonRainy_ICC$ICCs[1,2],3),", ",round(transpNonRainy_ICC$ICCs[1,3],3),")"),
                paste0(round(overall_ICC$ICCs[1,1],3)," (",round(overall_ICC$ICCs[1,2],3),", ",round(overall_ICC$ICCs[1,3],3),")"),
                paste0(round(resMed_ICC$ICCs[1,1],3)," (",round(resMed_ICC$ICCs[1,2],3),", ",round(resMed_ICC$ICCs[1,3],3),")"),
                paste0(round(comp_ICC$ICCs[1,1],3)," (",round(comp_ICC$ICCs[1,2],3),", ",round(comp_ICC$ICCs[1,3],3),")"),
                paste0(round(comp_trim_ICC$ICCs[1,1],3)," (",round(comp_trim_ICC$ICCs[1,2],3),", ",round(comp_trim_ICC$ICCs[1,3],3),")")
                ),
  "Avg.ICC" = c(paste0(round(terrainDiffNonR_ICC$ICCs[6,1],3)," (",round(terrainDiffNonR_ICC$ICCs[6,2],3),", ",round(terrainDiffNonR_ICC$ICCs[6,3],3),")"),
                paste0(round(terrainDiffR_ICC$ICCs[6,1],3)," (",round(terrainDiffR_ICC$ICCs[6,2],3),", ",round(terrainDiffR_ICC$ICCs[6,3],3),")"),
                paste0(round(roadcondR_ICC$ICCs[6,1],3)," (",round(roadcondR_ICC$ICCs[6,2],3),", ",round(roadcondR_ICC$ICCs[6,3],3),")"),
                paste0(round(roadcondnonR_ICC$ICCs[6,1],3)," (",round(roadcondnonR_ICC$ICCs[6,2],3),", ",round(roadcondnonR_ICC$ICCs[6,3],3),")"),
                paste0(round(timeRainy_ICC$ICCs[6,1],3)," (",round(timeRainy_ICC$ICCs[6,2],3),", ",round(timeRainy_ICC$ICCs[6,3],3),")"),
                paste0(round(timeNonRainy_ICC$ICCs[6,1],3)," (",round(timeNonRainy_ICC$ICCs[6,2],3),", ",round(timeNonRainy_ICC$ICCs[6,3],3),")"),
                paste0(round(transpRainy_ICC$ICCs[6,1],3)," (",round(transpRainy_ICC$ICCs[6,2],3),", ",round(transpRainy_ICC$ICCs[6,3],3),")"),
                paste0(round(transpNonRainy_ICC$ICCs[6,1],3)," (",round(transpNonRainy_ICC$ICCs[6,2],3),", ",round(transpNonRainy_ICC$ICCs[6,3],3),")"),
                paste0(round(overall_ICC$ICCs[6,1],3)," (",round(overall_ICC$ICCs[6,2],3),", ",round(overall_ICC$ICCs[6,3],3),")"),
                paste0(round(resMed_ICC$ICCs[6,1],3)," (",round(resMed_ICC$ICCs[6,2],3),", ",round(resMed_ICC$ICCs[6,3],3),")"),
                paste0(round(comp_ICC$ICCs[6,1],3)," (",round(comp_ICC$ICCs[6,2],3),", ",round(comp_ICC$ICCs[6,3],3),")"),
                paste0(round(comp_trim_ICC$ICCs[6,1],3)," (",round(comp_trim_ICC$ICCs[6,2],3),", ",round(comp_trim_ICC$ICCs[6,3],3),")")
                )
)

```


```{r, echo=F,include=F}

# Feasibility 
 
# For feasibility purposes, the time taken filling n villages will be divided by the number of villages answered by the judge
## Disclaimer: Even if a village assessment was discarded from the analysis due to 
## data entry issues, the time taken to fill the form will be taken into account in its entiriety


time_taken <- c()
for(i in sort(unique(data$`form.nVillages`))) 
    time_taken = append(time_taken,mean(data[which(data$`form.nVillages`==i),"Time_taken"]*60*24) %>% round()/i)



workload_df = aggregate(data[data$`form.nVillages`<10,
                             c("workloadEstimate")],
                        by=list(data[data$`form.nVillages`<10,]$username,
                                data[data$`form.nVillages`<10,]$formid),FUN = function(x) { 
    ux <- unique(x)
    ux[which.max(tabulate(match(x, ux)))]
    }  )

workload_df$estim = ifelse(workload_df[,3] ==1,"3. Survey felt laboursome",
                           ifelse(workload_df[,3] ==2,"2. Workload was moderate",
                                  ifelse(workload_df[,3] ==3,"1. Workload was light",NA)) )




# Example data
counts <- c(nrow(workload_df[which(workload_df[,3]==1),]),
            nrow(workload_df[which(workload_df[,3]==2),]), 
            nrow(workload_df[which(workload_df[,3]==3),]))
categories <- c("3. Survey felt laboursome", "2. Workload was moderate", "1. Workload was light")

# Calculate percentages
percentages <- counts / sum(counts) * 100


# Save numbers
nAssessments = nrow(data)

nAssessmentsPerRater = mean(aggregate(data$VillageID,by=list(data$username),FUN = function(x) length(unique(x)))[,2]) %>% round(3)

nAssessmentsPerVillage = mean(aggregate(data$hard_overall,by=list(data$VillageID),FUN = function(x) length(unique(x)))[,2]) %>% round(0)

nRatersPerVillage = mean(aggregate(data$hard_overall,by=list(data$VillageID),FUN = function(x) length(unique(x)))[,2]) %>% round(4)

nVillages = data[,c("District","cscom","villageName")] %>% distinct() %>% nrow()
nJudges = data$username %>% unique() %>% length()
nVillagesWithManyAssessments = data[,c("District","cscom","villageName")] %>% dplyr::count(District,cscom,villageName) %>% dplyr::filter(n >1)  %>% nrow()

minTime = min(time_taken)  ## to output
maxTime = max(time_taken)  ## to output
meanTime = mean(time_taken)  ## to output


# 2. Internal consistency
## Correlation plot



scaleItems = c("hard_overall","hard_residentsMedical",
               "hard_roadconditionNonRainyCar","hard_roadconditionRainyCar",
               "hard_timeTabletPlaceNonRainy","hard_timeTabletPlaceRainy",
               "hard_transportationEquipmentNonRainy","hard_transportationEquipmentRainy",
               "hard_terrainDifficultyNonRainy","hard_terrainDifficultyRainy")


polyChorData = na.omit(data[which(
  rowSums(data[,scaleItems[1:8]]==6,na.rm=T)==0
  ),scaleItems[1:8]])

for(i in 1:ncol(polyChorData)) {
  polyChorData[,i] = ifelse(polyChorData[,i]=="---" | 
                              polyChorData[,i]=="99",NA,polyChorData[,i]) %>% as.numeric()
}

polyChorData = na.omit(polyChorData)

polyMatrix = polychoric(polyChorData)$rho


mapDF = cbind.data.frame(scaleItems,c(
  "How hard this village \nis to reach?",
  "How difficult it is for the residents \nto seek medical care?",
  "Condition of the roads in non-rainy season",
  "Condition of the roads in rainy season",
  "How long does it take for you to \nget to this village on non-rainy season?",
  "How long does it take for you to \nget to this village on rainy season?",
  "How difficult it is to transport equipment \nto this village on non-rainy season?",
  "How difficult it is to transport equipment \nto this village on rainy season?",
  "How difficult is the terrain \nduring non-rainy season?",
  "How difficult is the terrain \nduring rainy season?"),
  c("How hard this village \nis to reach?",
    "How difficult it is for the residents \nto seek medical care?",
    "Condition of the roads in non-rainy season",
    "Condition of the roads in rainy season",
    "How long does it take for you to \nget to this village on non-rainy season?",
    "How long does it take for you to \nget to this village on rainy season?",
    "How difficult it is to transport equipment \nto this village on non-rainy season?",
    "How difficult it is to transport equipment \nto this village on rainy season?",
    "How difficult is the terrain \nduring non-rainy season?",
    "How difficult is the terrain \nduring rainy season?"))
names(mapDF) = c("Variable name","question","number")

for(i in scaleItems){
  data[,i] = as.numeric(ifelse(data[,i]=="---",NA,data[,i]) ) #+ rnorm(as.numeric(data[,i]),0,0.1)
  data[,i] = ifelse(data[,i]==99,6,data[,i])
  
}

corDF = data.frame("x.item"=NA,"y.item"=NA,"correlation" =NA,
                   "polyCor"=NA)
## Make correlation matrix 
for(x in scaleItems[1:8] ) {
  for(y in scaleItems[1:8]) {
    tempDF = data.frame("x.item"=x,"y.item"=y,"correlation"=cor(data[,x],
                                                                data[,y],
                                                                use="complete.obs",
                                                                method = "pearson"),
                        "polyCor"= polyMatrix[which(
                          row.names(polyMatrix)==x),y] )
    
    
    
    corDF = rbind.data.frame(corDF,tempDF)
  }
  
}

corDF = na.omit(corDF)

corDF = merge(corDF,mapDF[,c(1,3)],by.x="x.item",by.y = "Variable name",all.x=T)
names(corDF) = c("x.item","y.item","correlation","polyCor","x.descr")
corDF = merge(corDF,mapDF[,c(1,2)],by.x="y.item",by.y = "Variable name",all.x=T)
names(corDF) = c("y.item","x.item","correlation","polyCor","x.descr","y.descr")

corDF <- corDF %>%
  mutate(y.item_index = as.numeric(factor(y.descr)),
         x.item_index = as.numeric(factor(x.descr))) 

corDF = corDF[order(corDF$y.item_index,corDF$x.item_index),]

#corDF$correlation = ifelse(corDF$y.item_index<corDF$x.item_index,NA,corDF$correlation) 
corDF$polyCor = ifelse(corDF$y.item_index<corDF$x.item_index,NA,corDF$polyCor)
   


corplot = ggplot(corDF, aes(x = `x.descr`, y = `y.descr`, fill = polyCor)) +
  geom_tile(color = "white") +
  geom_text(aes(label = ifelse(is.na(polyCor), " ",formatC(round(polyCor, 2) , format = "f", digits = 2 ) ) ), color = "black", size = 6) +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Polychoric Correlation",na.value="white") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 15, hjust = 1,face = "bold"),
        axis.text.y = element_text(angle = 0, vjust = 1, 
                                   size = c(15,15,15,15,15,15,15,15,15), 
                                   hjust = 1,face = "bold",
                                   color=c(1,1,1,1,1,1,1,1))) + 
  xlab("") + ylab("") + ggtitle("Polychoric correlation matrix \nof the survey items",
                                subtitle = "Villages that can be reached by a vehicle") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  theme(plot.subtitle = element_text(size = 20)) +
  coord_fixed() 



histogram = ggplot(corDF[which(corDF$polyCor<.99999),], aes(x = polyCor )) +
  geom_histogram(aes(fill=..x..)) + theme_classic() +
  scale_fill_gradient(low = "purple", high = "blue") + 
  geom_density(color = "blue", size = 1) +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Correlation",na.value="white") + ylab("")+
  theme(legend.position = "none") + xlab("Polychoric correlation")


hist_grob = ggplotGrob(histogram)


scaleItems = c("hard_overall","hard_residentsMedical",
               "hard_terrainDifficultyNonRainy","hard_terrainDifficultyRainy",
               "hard_timeTabletPlaceNonRainy","hard_timeTabletPlaceRainy",
               "hard_transportationEquipmentNonRainy","hard_transportationEquipmentRainy")


polyChorData = na.omit(data[which(
  rowSums(data[,scaleItems[1:8]]==6,na.rm=T)==0
  ),scaleItems[1:8]])

for(i in 1:ncol(polyChorData)) {
  polyChorData[,i] = ifelse(polyChorData[,i]=="---" | 
                              polyChorData[,i]=="99",NA,polyChorData[,i]) %>% as.numeric()
}

polyChorData = na.omit(polyChorData)

polyMatrix = polychoric(polyChorData,correct=F)$rho


mapDF = cbind.data.frame(scaleItems,c(
  "How hard this village \nis to reach?",
  "How difficult it is for the residents \nto seek medical care?",
  "How difficult is the terrain \nduring non-rainy season?",
  "How difficult is the terrain \nduring rainy season?",
  "How long does it take for you to \nget to this village on non-rainy season?",
  "How long does it take for you to \nget to this village on rainy season?",
  "How difficult it is to transport equipment \nto this village on non-rainy season?",
  "How difficult it is to transport equipment \nto this village on rainy season?"),
  c("How hard this village \nis to reach?",
    "How difficult it is for the residents \nto seek medical care?",
    "How difficult is the terrain \nduring non-rainy season?",
    "How difficult is the terrain \nduring rainy season?",
    "How long does it take for you to \nget to this village on non-rainy season?",
    "How long does it take for you to \nget to this village on rainy season?",
    "How difficult it is to transport equipment \nto this village on non-rainy season?",
    "How difficult it is to transport equipment \nto this village on rainy season?"))
names(mapDF) = c("Variable name","question","number")

for(i in scaleItems){
  data[,i] = as.numeric(ifelse(data[,i]=="---",NA,data[,i]) ) #+ rnorm(as.numeric(data[,i]),0,0.1)
  data[,i] = ifelse(data[,i]==99,6,data[,i])
  
}

corDF = data.frame("x.item"=NA,"y.item"=NA,"correlation" =NA,
                   "polyCor"=NA)
## Make correlation matrix 
for(x in scaleItems[1:8] ) {
  for(y in scaleItems[1:8]) {
    tempDF = data.frame("x.item"=x,"y.item"=y,"correlation"=cor(data[,x],
                                                                data[,y],
                                                                use="complete.obs",
                                                                method = "pearson"),
                        "polyCor"= polyMatrix[which(
                          row.names(polyMatrix)==x),y] )
    
    
    
    corDF = rbind.data.frame(corDF,tempDF)
  }
  
}

corDF = na.omit(corDF)

corDF = merge(corDF,mapDF[,c(1,3)],by.x="x.item",by.y = "Variable name",all.x=T)
names(corDF) = c("x.item","y.item","correlation","polyCor","x.descr")
corDF = merge(corDF,mapDF[,c(1,2)],by.x="y.item",by.y = "Variable name",all.x=T)
names(corDF) = c("y.item","x.item","correlation","polyCor","x.descr","y.descr")

corDF <- corDF %>%
  mutate(y.item_index = as.numeric(factor(y.descr)),
         x.item_index = as.numeric(factor(x.descr))) 

corDF = corDF[order(corDF$y.item_index,corDF$x.item_index),]

#corDF$correlation = ifelse(corDF$y.item_index<corDF$x.item_index,NA,corDF$correlation) 
corDF$polyCor = ifelse(corDF$y.item_index<corDF$x.item_index,NA,corDF$polyCor)
   


corplot2 = ggplot(corDF, aes(x = `x.descr`, y = `y.descr`, fill = polyCor)) +
  geom_tile(color = "white") +
  geom_text(aes(label = ifelse(is.na(polyCor), " ",formatC(round(polyCor, 2) , format = "f", digits = 2 ) ) ), color = "black", size = 6) +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Polychoric Correlation",na.value="white") +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 15, hjust = 1,face = "bold"),
        axis.text.y = element_text(angle = 0, vjust = 1, 
                                   size = c(15,15,15,15,15,15,15,15,15), 
                                   hjust = 1,face = "bold",
                                   color=c(1,1,1,1,1,1,1,1))) + 
  xlab("") + ylab("") + ggtitle("Polychoric correlation matrix \nof the survey items",
                                subtitle = "Villages that can't be reached by a vehicle") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  theme(plot.subtitle = element_text(size = 20)) +
  coord_fixed() 



histogram2 = ggplot(corDF[which(corDF$polyCor<.99999),], aes(x = polyCor )) +
  geom_histogram(aes(fill=..x..)) + theme_classic() +
  scale_fill_gradient(low = "purple", high = "blue") + 
  geom_density(color = "blue", size = 1) +
  scale_fill_gradient2(low = "red", high = "blue", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Correlation",na.value="white") + ylab("")+
  theme(legend.position = "none") + xlab("Polychoric correlation")


hist_grob2 = ggplotGrob(histogram2)








strAV_mod = glmer(as.factor(strategieAvance) ~ scale(composite_full) + (1|username),data = data, family = "binomial") %>% summary()

strAV_mod_2 = glmer(as.factor(strategieAvance) ~ scale(composite_trim) + (1|username),data = data, family = "binomial") %>% summary()

dist_mod = lmer(scale(distanceKM) ~ scale(composite_full) + (1|username),data = data) %>% summary() ## to output

dist_mod_2 = lmer(scale(distanceKM) ~ scale(composite_trim) + (1|username),data = data) %>% summary() ## to output

rain_mod = lmer(scale(rain) ~ scale(composite_full) + (1|username),data = data) %>% summary()

rain_mod_2 = lmer(scale(rain) ~ scale(composite_trim) + (1|username),data = data) %>% summary()

travel_mod = lmer(scale(travel_time_car_minutes) ~ scale(composite_full) + (1|username),data = data) %>% summary()

travel_mod_2 = lmer(scale(travel_time_car_minutes) ~ scale(composite_trim) + (1|username),data = data) %>% summary()



```

# Results




## Descriptives 

```{r, echo=F}

kableExtra::kable(descrTable)

```




## Mortality 

```{r, echo=F}

kableExtra::kable(mortality_res_df)

```




## Feasibility

Number of village assessments: `r nAssessments` 

Number of villages: `r nVillages` 

Number of villages with more than one assessments: `r nVillagesWithManyAssessments` 

Number of judges: `r nJudges`

Minimum time: `r minTime`

Maximum time: `r maxTime`

Average time: `r meanTime`






### Assessment of workload (Assessed fewer than 10 villages in a round):

```{r, echo=F,  fig.width = 6, fig.asp = 1, fig.cap="\\label{fig:figs}Supplementary Figure 3" }

# Create barplot
barplot(counts, names.arg = categories, ylim = c(0, max(counts) * 1.2), col = "skyblue")

# Add percentage labels
text(x = 1:length(counts), y = counts, label = paste0(round(percentages, 1), "%"), pos = 3, cex = 1.8, col = "blue")

```











```{r, echo=F,include=F}
time_taken <- c()
for(i in sort(unique(data$`form.nVillages`))) 
    time_taken = append(time_taken,mean(data[which(data$`form.nVillages`==i),"Time_taken"]*60*24) %>% round()/i)



workload_df = aggregate(data[data$`form.nVillages`>=10,
                             c("workloadEstimate")],
                        by=list(data[data$`form.nVillages`>=10,]$username,
                                data[data$`form.nVillages`>=10,]$formid),FUN = function(x) { 
    ux <- unique(x)
    ux[which.max(tabulate(match(x, ux)))]
    }  )

workload_df$estim = ifelse(workload_df[,3] ==1,"3. Survey felt laboursome",
                           ifelse(workload_df[,3] ==2,"2. Workload was moderate",
                                  ifelse(workload_df[,3] ==3,"1. Workload was light",NA)) )




# Example data
counts <- c(nrow(workload_df[which(workload_df[,3]==1),]),
            nrow(workload_df[which(workload_df[,3]==2),]), 
            nrow(workload_df[which(workload_df[,3]==3),]))
categories <- c("3. Survey felt laboursome", "2. Workload was moderate", "1. Workload was light")

# Calculate percentages
percentages <- counts / sum(counts) * 100


```





### Assessment of workload (Assessed 10 villages or more in a round):
```{r, echo=F,  fig.width = 6, fig.asp = 1, fig.cap="\\label{fig:figs}Supplementary Figure 3" }

# Create barplot
barplot(counts, names.arg = categories, ylim = c(0, max(counts) * 1.2), col = "skyblue")

# Add percentage labels
text(x = 1:length(counts), y = counts, label = paste0(round(percentages, 1), "%"), pos = 3, cex = 1.8, col = "blue")

```


## Inter-rater reliability and internal consistency

### Polychoric correlation matrix:
```{r,fig.width=11,fig.height=12, echo=F, fig.cap="\\label{fig:figs}Figure 2"   }
# Overlay the histogram onto the heatmap
p1 <- corplot +
  annotation_custom(grob = hist_grob, xmin = 4.5, xmax = 8.5, ymin = 0.5, ymax = 4.5)

p2 <- corplot2 +
  annotation_custom(grob = hist_grob2, xmin = 4.5, xmax = 8.5, ymin = 0.5, ymax = 4.5)

p1
#gridExtra::grid.arrange(p1, p2, nrow = 2)

```


```{r,fig.width=11,fig.height=12, echo=F, fig.cap="\\label{fig:figs}Figure 2"   }
# Overlay the histogram onto the heatmap
p2
#gridExtra::grid.arrange(p1, p2, nrow = 2)

```



## Convergent validity

### Strategie Avance:
```{r,echo=FALSE, fig.dim = c(8, 9.5), fig.align = 'right'}

par(mfrow=c(3,2))



boxplot(data$composite_full~data$strategieAvance,xlab = "Strategié Avancé",
        ylab="Hard-to-reach composite variable, all items")

boxplot(data$composite_trim~data$strategieAvance,xlab = "Strategié Avancé",
        ylab="Hard-to-reach composite variable, two items")


library(ggplot2)
library(dplyr)
library(viridis)

ggplot(data=
         data[which(!is.na(data$strategieAvance)),], aes(x=strategieAvance, y=composite_full)) +
    geom_violin(width=1.0) +
    geom_boxplot(width=0.1, color="black", alpha=0.2) +
    scale_fill_viridis(discrete = TRUE) +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("") + ylab("Hard-to-reach composite score, all items") +
    xlab("") + theme_classic()

ggplot(data=
         data[which(!is.na(data$strategieAvance)),], aes(x=strategieAvance, y=composite_trim)) +
    geom_violin(width=1.0) +
    geom_boxplot(width=0.1, color="black", alpha=0.2) +
    scale_fill_viridis(discrete = TRUE) +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    ggtitle("") + ylab("Hard-to-reach composite score, two items") +
    xlab("") + theme_classic()

```

## Convergent validity

### As-crow-flies:
```{r, echo=F,  fig.width = 6, fig.asp = 1, , fig.cap="\\label{fig:figs}Figure 3"   }
plot(data$distanceKM,data$composite_full,xlab="Distance",ylab="Composite variable",
     main="As-crow-flies distance vs Composite variable")
abline(lm(data$composite_full~data$distanceKM))
text(25,18,
     paste0(round(as.data.frame(dist_mod$coefficients)[2,1],2),"\n (",
            round(as.data.frame(dist_mod$coefficients)[2,1]-1.96*as.data.frame(dist_mod$coefficients)[2,2],2)," to ",
            round(as.data.frame(dist_mod$coefficients)[2,1]+1.96*as.data.frame(dist_mod$coefficients)[2,2],2),")"),cex=1.5)  

```



### Average monthly rainfall:
```{r, echo=F,  fig.width = 6, fig.asp = 1, , fig.cap="\\label{fig:figs}Figure 3"   }
plot(data$rain,data$composite_full,xlab="Average monthly rainfall",ylab="Composite variable",
     main="Average monthly rainfall vs Composite variable")
abline(lm(data$composite_full~data$rain))
text(100,18,
     paste0(round(as.data.frame(rain_mod$coefficients)[2,1],2),"\n (",
            round(as.data.frame(rain_mod$coefficients)[2,1]-1.96*as.data.frame(rain_mod$coefficients)[2,2],2)," to ",
            round(as.data.frame(rain_mod$coefficients)[2,1]+1.96*as.data.frame(rain_mod$coefficients)[2,2],2),")"),cex=1.5)  

```


### Travel time:
```{r, echo=F,  fig.width = 6, fig.asp = 1, , fig.cap="\\label{fig:figs}Figure 3"   }
plot(data$travel_time_car_minutes,data$composite_full,xlab="Travel time by car",ylab="Composite variable",
     main="Travel time by car vs Composite variable")
abline(lm(data$composite_full~data$travel_time_car_minutes))
text(100,18,
     paste0(round(as.data.frame(travel_mod$coefficients)[2,1],2),"\n (",
            round(as.data.frame(travel_mod$coefficients)[2,1]-1.96*as.data.frame(travel_mod$coefficients)[2,2],2)," to ",
            round(as.data.frame(travel_mod$coefficients)[2,1]+1.96*as.data.frame(travel_mod$coefficients)[2,2],2),")"),cex=1.5)  

```


## Inter-rater reliability

### ICC table

```{r, echo=F}

kableExtra::kable(ICC_df)

```




